---
title: "Final Project"
author: "Leah Schultz"
date: "12/20/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning = FALSE, message = FALSE}
library(dplyr)
library(lme4)
library(ggplot2)
library(merTools)
library(sjPlot)
library(broom)
library(tidyr)
library(lcmm)
library(plyr)
oysup <- read.csv("~/1-descriptives-and-graphs-leahschultz/oysup_teacher_self.csv")
purpose <- read.csv("~/Dropbox/Lab & Research/OYSUP Project/oysup_self.csv")

oysup <- oysup %>%
  dplyr::select(FAMID, extra_7s:extra_10s, agree_7s:agree_10s,
                consc_7s:consc_10s, neuro_7s:neuro_10s, open_7s:open_10s,extra_7t:extra_10t,
                agree_7t:agree_10t, consc_7t:consc_10t, neuro_7t:neuro_10t, open_7t:open_10t)
dems <- purpose %>%
  dplyr::select(SEX2, MPEDUC2)
oysup <- cbind(oysup, dems)
```

First, restructuring data:

```{r, warning = FALSE, message = FALSE}
oysup_long <- tbl_df(oysup) %>%
  gather(c(-FAMID, -SEX2, -MPEDUC2), key = "grade", value = "value") %>%
  separate(grade, into = c("variable", "grade"), sep = "_", convert = T) %>%
  separate(grade, into = c("grade", "source"), sep = -2) %>%
  mutate(grade = as.numeric(grade)) %>%
  spread(variable, value)
oysup_long
oysup_long$grade2 <- oysup_long$grade^2
```

As a complement to the SEM growth models and TICs models that I'm already doing for my analyses of personality change during adolescence, I want to use latent class mixed models to understand any consistent trends that might be occurring in individuals' development, both from student- and teacher-reports. It is clear that not everyone is changing in the same ways during this time, but are there distinct clusters of students changing in specific ways?

```{r, warning = FALSE, message = FALSE}
oysup_long_e <- subset(oysup_long, subset = !is.na(extra))
oysup_long_e_s <- subset(oysup_long_e, subset = source=="s")

model_1 <- lcmm(fixed = extra ~ grade + grade2, 
                   random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=1, idiag=FALSE, link="linear",data=oysup_long_e_s)

model_2 <- lcmm(fixed = extra ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=2, idiag=FALSE, link="linear",data=oysup_long_e_s)

model_3 <- lcmm(fixed = extra ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=3, idiag=FALSE, link="linear",data=oysup_long_e_s)

model_4 <- lcmm(fixed = extra ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=4, idiag=FALSE, link="linear",data=oysup_long_e_s)

model_5 <- lcmm(fixed = extra ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=5, idiag=FALSE, link="linear",data=oysup_long_e_s)
```

```{r, warning = FALSE, message = FALSE}
summarytable(model_1, model_2, model_3, model_4, model_5)
```
Looks like after 2 classes, a third class cannot be estimated. Two classes seem to fit the data best. Let's look at how many subjects are in each class (since it gives percentages but not #s).

```{r, warning = FALSE, message = FALSE}
# How many subjects per class in 2-class model?
pp_model2 <- postprob(model_2) 
pp_model2[1]
```



```{r, warning = FALSE, message = FALSE}

#First, we need a data frame that specifies which class subjects are in
membership <- as.data.frame(matrix(nrow=959,ncol=2))
colnames(membership) <- c("FAMID","Class_2")
membership[,1:2] <- model_2$pprob[,1:2]
oysup_long_e_s <- merge(x = oysup_long_e_s, y = membership, by="FAMID")

# How are the classes different?

# Extraversion in 7th grade
oysup_long_e_s7 <- subset(oysup_long_e_s, subset = grade=="7")
t.test(data = oysup_long_e_s7, extra ~ Class_2)

oysup_long_e_s8 <- subset(oysup_long_e_s, subset = grade=="8")
t.test(data = oysup_long_e_s8, extra ~ Class_2)

oysup_long_e_s9 <- subset(oysup_long_e_s, subset = grade=="9")
t.test(data = oysup_long_e_s9, extra ~ Class_2)

oysup_long_e_s10 <- subset(oysup_long_e_s, subset = grade=="10")
t.test(data = oysup_long_e_s10, extra ~ Class_2)

```

Group 2 is stable, while Group 1 is decreasing over time.

## Let's repeat with teacher-reported data.

```{r, warning = FALSE, message = FALSE}
oysup_long_e <- subset(oysup_long, subset = !is.na(extra))
oysup_long_e_t <- subset(oysup_long_e, subset = source=="t")

model_1 <- lcmm(fixed = extra ~ grade + grade2, 
                   random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=1, idiag=FALSE, link="linear",data=oysup_long_e_t)

model_2 <- lcmm(fixed = extra ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=2, idiag=FALSE, link="linear",data=oysup_long_e_t)

model_3 <- lcmm(fixed = extra ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=3, idiag=FALSE, link="linear",data=oysup_long_e_t)

model_4 <- lcmm(fixed = extra ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=4, idiag=FALSE, link="linear",data=oysup_long_e_t)

model_5 <- lcmm(fixed = extra ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=5, idiag=FALSE, link="linear",data=oysup_long_e_t)
```

```{r, warning = FALSE, message = FALSE}
summarytable(model_1, model_2, model_3, model_4, model_5)

pp_model2 <- postprob(model_2) 
pp_model2[1]

pp_model3 <- postprob(model_3) 
pp_model3[1]

pp_model4 <- postprob(model_4) 
pp_model4[1]

pp_model5 <- postprob(model_5) 
pp_model5[1]
```

A two-class solution seems to work best here, too.

```{r, warning = FALSE, message = FALSE}

membership <- as.data.frame(matrix(nrow=939,ncol=2))
colnames(membership) <- c("FAMID","Class_2")
membership[,1:2] <- model_2$pprob[,1:2]
oysup_long_e_t <- merge(x = oysup_long_e_t, y = membership, by="FAMID")

oysup_long_e_t7 <- subset(oysup_long_e_t, subset = grade=="7")
t.test(data = oysup_long_e_t7, extra ~ Class_2)

oysup_long_e_t8 <- subset(oysup_long_e_t, subset = grade=="8")
t.test(data = oysup_long_e_t8, extra ~ Class_2)

oysup_long_e_t9 <- subset(oysup_long_e_t, subset = grade=="9")
t.test(data = oysup_long_e_t9, extra ~ Class_2)

oysup_long_e_t10 <- subset(oysup_long_e_t, subset = grade=="10")
t.test(data = oysup_long_e_t10, extra ~ Class_2)
```
Once again, we have a higher group and a lower group, though it is difficult to see what exactly is happening at the individual-curve level unless we plot.

# Agreeableness

```{r, warning = FALSE, message = FALSE}
oysup_long_a <- subset(oysup_long, subset = !is.na(agree))
oysup_long_a_s <- subset(oysup_long_a, subset = source=="s")

model_1 <- lcmm(fixed = agree ~ grade + grade2, 
                   random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=1, idiag=FALSE, link="linear",data=oysup_long_a_s)

model_2 <- lcmm(fixed = agree ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=2, idiag=FALSE, link="linear",data=oysup_long_a_s)

model_3 <- lcmm(fixed = agree ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=3, idiag=FALSE, link="linear",data=oysup_long_a_s)

model_4 <- lcmm(fixed = agree ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=4, idiag=FALSE, link="linear",data=oysup_long_a_s)

model_5 <- lcmm(fixed = agree ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=5, idiag=FALSE, link="linear",data=oysup_long_a_s)
```

```{r, warning = FALSE, message = FALSE}
summarytable(model_1, model_2, model_3, model_4, model_5)
```
Two classes seem to fit the data best. Let's look at how many subjects are in each class.

```{r, warning = FALSE, message = FALSE}
# How many subjects per class in 2-class model?
pp_model2 <- postprob(model_2) 
pp_model2[1]
```

```{r, warning = FALSE, message = FALSE}
# How are the classes different?

membership <- as.data.frame(matrix(nrow=960,ncol=2))
colnames(membership) <- c("FAMID","Class_2")
membership[,1:2] <- model_2$pprob[,1:2]
oysup_long_a_s <- merge(x = oysup_long_a_s, y = membership, by="FAMID")

# agreeableness in 7th grade
oysup_long_a_s7 <- subset(oysup_long_a_s, subset = grade=="7")
t.test(data = oysup_long_a_s7, agree ~ Class_2)

# agreeableness in 8th grade
oysup_long_a_s8 <- subset(oysup_long_a_s, subset = grade=="8")
t.test(data = oysup_long_a_s8, agree ~ Class_2)

# agreeableness in 9th grade
oysup_long_a_s9 <- subset(oysup_long_a_s, subset = grade=="9")
t.test(data = oysup_long_a_s9, agree ~ Class_2)

# agreeableness in 10th grade
oysup_long_a_s10 <- subset(oysup_long_a_s, subset = grade=="10")
t.test(data = oysup_long_a_s10, agree ~ Class_2)

```

```{r, warning = FALSE, message = FALSE}
oysup_long_a_s$FAMID <- as.character(oysup_long_a_s$FAMID)
plot_a_s <- ggplot(oysup_long_a_s, aes(x = grade, y = agree, group = FAMID, color = Class_2)) +
  geom_smooth(aes(group = FAMID, color = Class_2), size = 0.5) +
  geom_smooth(aes(group = Class_2), method = "loess", size = 2, se=T)
plot_a_s
```

Again, one group seems to be relatively stable and high, while the other seems to decrease in agreeableness over time.

## Let's repeat with teacher-reported data.

```{r, warning = FALSE, message = FALSE}
oysup_long_a <- subset(oysup_long, subset = !is.na(agree))
oysup_long_a_t <- subset(oysup_long_a, subset = source=="t")

model_1 <- lcmm(fixed = agree ~ grade + grade2, 
                   random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=1, idiag=FALSE, link="linear",data=oysup_long_a_t)

model_2 <- lcmm(fixed = agree ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=2, idiag=FALSE, link="linear",data=oysup_long_a_t)

model_3 <- lcmm(fixed = agree ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=3, idiag=FALSE, link="linear",data=oysup_long_a_t)

model_4 <- lcmm(fixed = agree ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=4, idiag=FALSE, link="linear",data=oysup_long_a_t)

model_5 <- lcmm(fixed = agree ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=5, idiag=FALSE, link="linear",data=oysup_long_a_t)
```

```{r, warning = FALSE, message = FALSE}
summarytable(model_1, model_2, model_3, model_4, model_5)

pp_model3 <- postprob(model_3) 
pp_model3[1]

```

A three-class solution seems to work best here, actually.

```{r, warning = FALSE, message = FALSE}

membership <- as.data.frame(matrix(nrow=939,ncol=2))
colnames(membership) <- c("FAMID","Class_3")
membership[,1:2] <- model_3$pprob[,1:2]
oysup_long_a_t <- merge(x = oysup_long_a_t, y = membership, by="FAMID")

oysup_long_a_t7 <- subset(oysup_long_a_t, subset = grade=="7")
anova1 <- aov(formula = agree ~ Class_3, data = oysup_long_a_t7)
summary(anova1)

oysup_long_a_t8 <- subset(oysup_long_a_t, subset = grade=="8")
anova2 <- aov(formula = agree ~ Class_3, data = oysup_long_a_t8)
summary(anova2)

oysup_long_a_t9 <- subset(oysup_long_a_t, subset = grade=="9")
anova3 <- aov(formula = agree ~ Class_3, data = oysup_long_a_t9)
summary(anova3)

oysup_long_a_t10 <- subset(oysup_long_a_t, subset = grade=="10")
anova4 <- aov(formula = agree ~ Class_3, data = oysup_long_a_t10)
summary(anova4)
```
Once again, we have differences between groups, though it is difficult to see what exactly is happening at the individual-curve level unless we plot.

```{r, warning = FALSE, message = FALSE}
plot_a_t <- ggplot(oysup_long_a_t, aes(x = grade, y = agree, group = FAMID, color = Class_3)) +
  geom_smooth(aes(group = FAMID, color = Class_3), size = 0.5, se=F) +
  geom_smooth(aes(group = Class_3), method = "loess", size = 2, se=T)
plot_a_t
```


