---
title: "Final Project"
author: "Leah Schultz"
date: "12/20/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning = FALSE, message = FALSE}
library(dplyr)
library(lme4)
library(ggplot2)
library(merTools)
library(sjPlot)
library(broom)
library(tidyr)
library(lcmm)
library(plyr)
oysup <- read.csv("~/1-descriptives-and-graphs-leahschultz/oysup_teacher_self.csv")
purpose <- read.csv("~/Dropbox/Lab & Research/OYSUP Project/oysup_self.csv")

oysup <- oysup %>%
  dplyr::select(FAMID, extra_7s:extra_10s, agree_7s:agree_10s,
                consc_7s:consc_10s, neuro_7s:neuro_10s, open_7s:open_10s,extra_7t:extra_10t,
                agree_7t:agree_10t, consc_7t:consc_10t, neuro_7t:neuro_10t, open_7t:open_10t)
dems <- purpose %>%
  dplyr::select(SEX2, MPEDUC2)
oysup <- cbind(oysup, dems)
```

First, restructuring data:

```{r}
oysup_long <- tbl_df(oysup) %>%
  gather(c(-FAMID, -SEX2, -MPEDUC2), key = "grade", value = "value") %>%
  separate(grade, into = c("variable", "grade"), sep = "_", convert = T) %>%
  separate(grade, into = c("grade", "source"), sep = -2) %>%
  mutate(grade = as.numeric(grade)) %>%
  spread(variable, value)
oysup_long
oysup_long$grade2 <- oysup_long$grade^2
```

As a complement to the SEM growth models and TICs models that I'm already doing for my analyses of personality change during adolescence, I want to use latent class mixed models to understand any consistent trends that might be occurring in individuals' development, both from student- and teacher-reports. It is clear that not everyone is changing in the same ways during this time, but are there distinct clusters of students changing in specific ways?

```{r}
oysup_long_e <- subset(oysup_long, subset = !is.na(extra))
oysup_long_e_s <- subset(oysup_long_e, subset = source=="s")

model_1 <- lcmm(fixed = extra ~ grade + grade2, 
                   random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=1, idiag=FALSE, link="linear",data=oysup_long_e_s)

model_2 <- lcmm(fixed = extra ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=2, idiag=FALSE, link="linear",data=oysup_long_e_s)

model_3 <- lcmm(fixed = extra ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=3, idiag=FALSE, link="linear",data=oysup_long_e_s)

model_4 <- lcmm(fixed = extra ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=4, idiag=FALSE, link="linear",data=oysup_long_e_s)

model_5 <- lcmm(fixed = extra ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=5, idiag=FALSE, link="linear",data=oysup_long_e_s)
```

```{r}
summarytable(model_1, model_2, model_3, model_4, model_5)
```
Looks like after 2 classes, a third class cannot be estimated. Two classes seem to fit the data best. Let's look at how many subjects are in each class (since it gives percentages but not #s).

```{r}
# How many subjects per class in 2-class model?
pp_model2 <- postprob(model_2) 
pp_model2[1]
```



```{r}
# Simple plotting
#plot.lcmm(model_1,which="fit",var.time="grade",bty="n")

#First, we need a data frame that specifies which class subjects are in
membership <- as.data.frame(matrix(nrow=959,ncol=2))
colnames(membership) <- c("FAMID","Class_2")
membership[,1:2] <- model_2$pprob[,1:2]
oysup_long_e_s <- merge(x = oysup_long_e_s, y = membership, by="FAMID")

# How are the classes different?

# Extraversion in 7th grade
oysup_long_e_s7 <- subset(oysup_long_e_s, subset = grade=="7")
t.test(data = oysup_long_e_s7, extra ~ Class_2)

oysup_long_e_s8 <- subset(oysup_long_e_s, subset = grade=="8")
t.test(data = oysup_long_e_s8, extra ~ Class_2)

oysup_long_e_s9 <- subset(oysup_long_e_s, subset = grade=="9")
t.test(data = oysup_long_e_s9, extra ~ Class_2)

oysup_long_e_s10 <- subset(oysup_long_e_s, subset = grade=="10")
t.test(data = oysup_long_e_s10, extra ~ Class_2)

```

Group 2 is stable, while Group 1 is decreasing over time.

## Let's repeat with teacher-reported data.

```{r}
oysup_long_e <- subset(oysup_long, subset = !is.na(extra))
oysup_long_e_s <- subset(oysup_long_e, subset = source=="s")

model_1 <- lcmm(fixed = extra ~ grade + grade2, 
                   random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=1, idiag=FALSE, link="linear",data=oysup_long_e_s)

model_2 <- lcmm(fixed = extra ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=2, idiag=FALSE, link="linear",data=oysup_long_e_s)

model_3 <- lcmm(fixed = extra ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=3, idiag=FALSE, link="linear",data=oysup_long_e_s)

model_4 <- lcmm(fixed = extra ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=4, idiag=FALSE, link="linear",data=oysup_long_e_s)

model_5 <- lcmm(fixed = extra ~ grade + grade2, 
                   mixture = ~grade, random = ~grade, nwg = FALSE, subject = "FAMID",
                   ng=5, idiag=FALSE, link="linear",data=oysup_long_e_s)
```

```{r}
summarytable(model_1, model_2, model_3, model_4, model_5)
```

```{r}
oysup_long_e_s7 <- subset(oysup_long_e_s, subset = grade=="7")
t.test(data = oysup_long_e_s7, extra ~ Class_2)

oysup_long_e_s8 <- subset(oysup_long_e_s, subset = grade=="8")
t.test(data = oysup_long_e_s8, extra ~ Class_2)

oysup_long_e_s9 <- subset(oysup_long_e_s, subset = grade=="9")
t.test(data = oysup_long_e_s9, extra ~ Class_2)

oysup_long_e_s10 <- subset(oysup_long_e_s, subset = grade=="10")
t.test(data = oysup_long_e_s10, extra ~ Class_2)
```

