---
title: "Homework 2"
author: "Leah Schultz"
date: "9/28/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Chapter 3: Growth Curves
```{r loading, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(lme4)
library(ggplot2)
library(broom)
library(merTools)
library(sjPlot)
oysup <- read.csv("~/1-descriptives-and-graphs-leahschultz/oysup_teacher_self.csv")
purpose <- read.csv("~/Dropbox/Lab & Research/OYSUP Project/oysup_self.csv")
oysup <- oysup %>%
  dplyr::select(FAMID, neuro_7s:neuro_10s)
dems <- purpose %>%
  dplyr::select(SEX2)
oysup <- cbind(oysup, dems)
```

First, restructuring data:

```{r}
oysup_long <- tbl_df(oysup) %>%
  gather(c(neuro_7s:neuro_10s), key = "grade", value = "value") %>%
  separate(grade, into = c("variable", "grade"), sep = "_", convert = T) %>%
  separate(grade, into = c("grade", "delete"), sep = "s") %>%
  mutate(grade = as.numeric(grade)) %>%
  dplyr::select(-delete) %>%
  spread(variable, value)
oysup_long
```

## 1. Run linear models on all of your subjects (a basic regression). What is the average intercept, the average slope?

```{r}
model1 <- lm(neuro ~ grade, data = oysup_long)
summary(model1)
```

### Average intercept = 3.53

### Average slope = -.04

## 2. Now run a mlm/lmer model with only a random intercept.
```{r}
model2 <- lmer(neuro ~ (1 | FAMID), data = oysup_long)
summary(model2)
```

## 3. What is the ICC?

### ICC = % between- vs. within-person variance

### variance by ID / variance by ID + residual variance

### .50 / (.50 + .60) = .45


## What does residual variance look like compared to linear model? Create a graph to show this effect.

```{r warning=FALSE}
model1.aug <- augment(model1)
model2.aug <- augment(model2)
mod1_resid <- abs(model1.aug$.resid)
mod2_resid <- abs(model2.aug$.resid)
mean_mod1 <- mean(mod1_resid)
mean_mod2 <- mean(mod2_resid)
resid_df <- data.frame("Type" = c("Linear", "Mixed"), 
                       "Mean" = c(mean_mod1, mean_mod2))
resid_plot <- ggplot(resid_df, aes(x = Type, y = Mean)) +
  geom_col(width = .5)
resid_plot
```

### Average residual variance is lower in the mixed model, since we're accounting for individual-level, random effects.

## 3. Introduce a fixed slope term. What is the difference in terms of the fixed effects estimates between this estimate and the previous? Of the residual standard error? Create a graph to show both fixed effects estimates and the CIs around them.

```{r}
model3 <- lmer(neuro ~ grade + (1 | FAMID), data = oysup_long)
summary(model3)

fixef(model2) - fixef(model3)[1]

fe_2 <- tidy(model2, effects = "fixed", conf.int = T, conf.level = 0.95)
fe_3 <- tidy(model3, effects = "fixed", conf.int = T, conf.level = 0.95)

fe_df <- data.frame("Parameter" = c("Model 1: Intercept", "Model 2: Intercept", "Model 2: Slope"),
                    "Fixed_Effects" = c(fe_2$estimate, fe_3[1,2], fe_3[2,2]),
                    "Lower_CI" = c(fe_2$conf.low, fe_3[1,5], fe_3[2,5]),
                    "Upper_CI" = c(fe_2$conf.high, fe_3[1,6], fe_3[2,6]),
                    "Model" = c("1", "2", "2"))

fe_plot <- ggplot(fe_df, aes(x = Parameter, y = Fixed_Effects)) +
  geom_col(aes(fill = Model)) +
  geom_errorbar(aes(ymin = Lower_CI, ymax = Upper_CI))
fe_plot

sigma(model2) - sigma(model3)[1]
```

### Fixed effect estimate for intercept increased by .37 points from 3.20 to 3.57.

### Residual standard error decreased by .002. Seems like adding a fixed slope term did not do much to improve the model.

## 4. Run an additional model with a random slope. How does this change compare to the previous model? Should you keep the random slope or not?

```{r}
model4 <- lmer(neuro ~ grade + (1 + grade | FAMID), data = oysup_long)
summary(model4)

sigma(model3)[1] - sigma(model4)[1]
anova(model3, model4)
```

### The residual error decreases .03 with the addition of a random slope. A likelihood ratio test indicates that the model fit is better with this new parameter, as well. I'll keep the random slope.

## 5. Interpret the correlation between the slope and the intercept.

### Correlation between slope and intercept = -.97. Adolescents who are initially higher on neuroticism will tend to decrease over time compared to children who are initially lower on neuroticism.

## 6. Create a density plot of the random effects from your final model.

```{r}
random_params <- tidy(model4, effect = "ran_modes")

raneff_plot <- ggplot(random_params, aes(x = estimate, color = term)) +
  geom_density()

raneff_plot
```

## 7. Create a caterpillar plot of the random effects. Is there any person that seems odd in terms of large standard errors around intercept and slope estimates?

```{r}
re.sim <- REsim(model4)
plotREsim(re.sim)
```

### It looks as if there are about many individuals who deviate from the fixed slope, and are thus driving the model to be better represented by a random slope. There is only one student who seems to deviate notably from the fixed intercept.


## 8. Create a plot of the trajectory, along with a spaghetti plot of each person’s individual slope. Set the alpha level (transparency) on the individual slopes to make them easier to see.

```{r warning=FALSE}
predict <- predictInterval(merMod = model4, newdata = oysup_long,
                           level = 0.9, n.sims = 100, 
                           stat = "median", include.resid.var = TRUE)
growth_df <- cbind(oysup_long, predict$fit)

growth_plot <- ggplot(oysup_long, aes(x = grade, y = predict$fit)) +
  geom_line(aes(group = FAMID), alpha = .2) +
  stat_smooth(method = lm) +
  theme_bw()+
  xlab("Grade")+
  ylab("Self-Reported Neuroticism")+
  ylim(1,5)
growth_plot
```

