---
title: "Homework 1"
author: "Leah Schultz"
date: "9/28/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Chapter 2: LDA Basics
```{r loading, message=FALSE, warning=FALSE}
library(tidyr)
library(ggplot2)
library(dplyr)
oysup <- read.csv("~/1-descriptives-and-graphs-leahschultz/oysup_teacher_self.csv")
purpose <- read.csv("~/Dropbox/Lab & Research/OYSUP Project/oysup_self.csv")
oysup <- oysup %>%
  dplyr::select(FAMID, neuro_7s:neuro_10s)
dems <- purpose %>%
  dplyr::select(SEX2)
oysup <- cbind(oysup, dems)
```

## 1. Move your data into a long format and a wide format. Did you have any specific challenges that you encountered? If so, discuss them.

```{r #1}
oysup_long <- tbl_df(oysup) %>%
  gather(c(neuro_7s:neuro_10s), key = "grade", value = "value") %>%
  separate(grade, into = c("variable", "grade"), sep = "_", convert = T) %>%
  separate(grade, into = c("grade", "delete"), sep = "s") %>%
  dplyr::select(-delete) %>%
  spread(variable, value)
oysup_long

oysup_wide <- tbl_df(oysup_long) %>%
  gather(-c(FAMID, SEX2, grade), key = "variable", value = "value") %>%
  unite(VarG, variable, grade)  %>%
  spread(key = VarG, value = value) %>%
  select_if(~sum(!is.na(.)) > 0)
oysup_wide
```

Challenges: First I forgot to exclude the ID variable and stable demographics, so R tried to make it into a value. I had a lot of variables that had repeated measures, so I had to think about how to split them after I gathered everything. Also, my variables were not consistently named because I was mixing naming conventions (my preferred conventions, and then the ones that OPP used). I went in and cleaned up my file a lot more so that I could use the separate function easily in the next step.

Another thing that was difficult was I ended up with some NA columns when I spread my data back to wide format -- the drop and fill arguments didn't seem to help, so I had to find a solution for how to drop the NA columns from the key-pair combinations that didn't exist (for example, oysup wasn't assessed at grade 1).


## 2. Create a wave variable and date variable (if applicable).
I already have a grade variable, which is equivalent to wave for my purposes, and do not have dates available beyond year, which is not very useful.

## 3. What is your sample size for each wave of assessment?

```{r}
oysup_long %>% 
  group_by(grade) %>%
  filter(!is.na(neuro)) %>%
  count()
```

## 4. Take the date variable and convert it to a different date format such as time in study or age (if appropriate). What scale is most suitable for your analyses? (weeks/months/years?)

Not applicable for my analyses.

## 5. Graph your data using the different time metrics, fitting individual curves for each person.

Plotting individual curves for neuroticism over time:
```{r, warning=F}
gg2 <- ggplot(oysup_long, aes(x = grade, y = neuro, group=FAMID)) +
  geom_line() +
  aes(colour = factor(FAMID)) + guides(colour=FALSE) +
  scale_x_discrete(limits = c("7","8","9","10"))
gg2
```

Predicted values should look a little better, because each time point is an average of just two values...

```{r, warning=F}
## Subset of 10 curves
set.seed(11)
ex.random <- oysup_long %>% 
  dplyr::select(FAMID) %>% 
  distinct %>% 
  sample_n(10) 

example <-
  left_join(ex.random, oysup_long) 

gg4 <- ggplot(example, aes(x = grade, y = neuro, group = FAMID)) + 
  geom_point() + stat_smooth(method="lm") + facet_wrap(~FAMID) +
  ylim(1,5)+
  scale_x_discrete(limits = c("7","8","9","10"))
gg4
```

## 6. Create an overall average trend of your data (split up into groups if appropriate). Attempt to color your individual data points and/or shade different lines (highlight some participants, highlight the average trend line but not the individual level lines).

```{r, warning=F}

gg5 <- ggplot(oysup_long, aes(x = jitter(as.numeric(grade)), y = neuro)) +
  geom_point() + stat_smooth() 
gg5
```

## 7. Look at the correlations of your DV across time.

```{r}
neuro <- oysup_wide %>%
  select(neuro_10:neuro_9)
cor(neuro, use = "complete.obs")
```

