---
title: "Homework 4 (SEM)"
author: "Leah Schultz"
date: "11/2/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Chapter 7: SEM
```{r warning = FALSE, message = FALSE}
library(lme4)
library(ggplot2)
library(lavaan)
oysup <- read.csv("~/Desktop/oysup_teacher_self.csv")
```

## 1) Fit a measurement model to your constructs at one time point. Try out the different types of scaling discussed in class. What changes? What stays the same?

```{r}
## Marker variable
mod.1 <- 'neuro_t =~ TPER7_08 + TPER7_10 + TPER7_17R + TPER7_12R + TPER7_13R'
fit.1 <- cfa(mod.1, data=oysup)
summary(fit.1, fit.measures=TRUE)

## Fixed factor
mod.2 <- 'neuro_t =~ TPER7_08 + TPER7_10 + TPER7_17R + TPER7_12R + TPER7_13R'
fit.2 <- cfa(mod.2, std.lv = T, data=oysup)
summary(fit.2, fit.measures=TRUE)

## Effects coding
mod.3 <- 'neuro_t =~ NA*TPER7_08 + L1*TPER7_08 + L2*TPER7_10 + L3*TPER7_17R + L4*TPER7_12R + L5*TPER7_13R
L1 == 5 - L2 - L3 - L4 - L5'
fit.3 <- cfa(mod.3, data=oysup)
summary(fit.3, fit.measures=TRUE)

```

Using the marker variable approach, the loading of the first factor onto the latent variable is fixed to 1, and the other loadings relative to this range from .64 to 1.19. The CFI is .94. Using the fixed factor approach, the item loadings change -- they range from .53 to .98. The residual variances of the items stay the same, but of course the variance of the latent neuroticism variable changes to 1. Using effects coding, the item loadings onto the latent variable change once more, ranging from .66 to 1.23, and the variance of the latent variable changes back to being freely estimated (.63).

## 2) What do the fit statistics say about your latent variable? Good/bad? Is your latent variable just identified/saturated, under-identified, or over-identified?

```{r}
fitMeasures(fit.1)
```

Across all approaches (regardless of scaling), the CFI is .94 (great!), while the RMSEA is .15 (poor). There are 5 degrees of freedom, meaning that the model is over-identified - yay.

## 3) Fit a longitudinal CFA model where you a) first correlate your latent factors across time and then b) a second model that predicts later times by a prevous time (i.e., auto-regressive; t1 -> t2 -> t3). What are your conclusions? How does one differ from the other?

```{r}
# Residuals correlated over time
mod.4 <- 'neuro_t1 =~ TPER7_08 + TPER7_10 + TPER7_17R + TPER7_12R + TPER7_13R
neuro_t2 =~ TPER8_08 + TPER8_10 + TPER8_17R + TPER8_12R + TPER8_13R
neuro_t3 =~ TPER9_08 + TPER9_10 + TPER9_17R + TPER9_12R + TPER9_13R
neuro_t4 =~ TPER10_08 + TPER10_10 + TPER10_17R + TPER10_12R + TPER10_13R

TPER7_08 ~~ TPER8_08 + TPER9_08 + TPER10_08
TPER8_08 ~~ TPER9_08 + TPER10_08
TPER9_08 ~~ TPER10_08

TPER7_10 ~~ TPER8_10 + TPER9_10 + TPER10_10
TPER8_10 ~~ TPER9_10 + TPER10_10
TPER9_10 ~~ TPER10_10

TPER7_17R ~~ TPER8_17R + TPER9_17R + TPER10_17R
TPER8_17R ~~ TPER9_17R + TPER10_17R
TPER9_17R ~~ TPER10_17R

TPER7_12R ~~ TPER8_12R + TPER9_12R + TPER10_12R
TPER8_12R ~~ TPER9_12R + TPER10_12R
TPER9_12R ~~ TPER10_12R

TPER7_13R ~~ TPER8_13R + TPER9_13R + TPER10_13R
TPER8_13R ~~ TPER9_13R + TPER10_13R
TPER9_13R ~~ TPER10_13R'
fit.4 <- cfa(mod.4, data=oysup)
summary(fit.4, fit.measures=TRUE)

# Auto-regressive model
mod.5 <- 'neuro_t1 =~ TPER7_08 + TPER7_10 + TPER7_17R + TPER7_12R + TPER7_13R
neuro_t2 =~ TPER8_08 + TPER8_10 + TPER8_17R + TPER8_12R + TPER8_13R
neuro_t3 =~ TPER9_08 + TPER9_10 + TPER9_17R + TPER9_12R + TPER9_13R
neuro_t4 =~ TPER10_08 + TPER10_10 + TPER10_17R + TPER10_12R + TPER10_13R

TPER7_08 ~~ TPER8_08 + TPER9_08 + TPER10_08
TPER8_08 ~~ TPER9_08 + TPER10_08
TPER9_08 ~~ TPER10_08

TPER7_10 ~~ TPER8_10 + TPER9_10 + TPER10_10
TPER8_10 ~~ TPER9_10 + TPER10_10
TPER9_10 ~~ TPER10_10

TPER7_17R ~~ TPER8_17R + TPER9_17R + TPER10_17R
TPER8_17R ~~ TPER9_17R + TPER10_17R
TPER9_17R ~~ TPER10_17R

TPER7_12R ~~ TPER8_12R + TPER9_12R + TPER10_12R
TPER8_12R ~~ TPER9_12R + TPER10_12R
TPER9_12R ~~ TPER10_12R

TPER7_13R ~~ TPER8_13R + TPER9_13R + TPER10_13R
TPER8_13R ~~ TPER9_13R + TPER10_13R
TPER9_13R ~~ TPER10_13R

neuro_t4 ~ neuro_t3
neuro_t3 ~ neuro_t2
neuro_t2 ~ neuro_t1'
fit.5 <- cfa(mod.5, data=oysup)
summary(fit.5, fit.measures=TRUE)
```

Based on CFI and RSMEA values, the auto-regressive model fits the data a bit poorer than the other. 

## 4) Fit a longitudinal growth model in SEM and in HLM. Compare and contrast the differences.

```{r}
# SEM
model.6 <- 'neuro_i =~ 1*neuro_7t + 1*neuro_8t + 1*neuro_9t + 1*neuro_10t
            neuro_s =~ 0*neuro_7t + 1*neuro_8t + 2*neuro_9t + 3*neuro_10t'
fit.6 <- growth(model.6, data = oysup)
summary(fit.6)

# restructuring for HLM
oysup_long <- tbl_df(oysup) %>%
  gather(c(neuro_7t:neuro_10t), key = "grade", value = "value") %>%
  separate(grade, into = c("variable", "grade"), sep = "_", convert = T) %>%
  separate(grade, into = c("grade", "delete"), sep = "t") %>%
  mutate(grade = as.numeric(grade)) %>%
  dplyr::select(-delete) %>%
  spread(variable, value)

# HLM
model.7 <- lmer(neuro ~ 1 + grade + (1 + grade | FAMID), data=oysup_long)
summary(model.7)
```

Both models estimate the average slope at about -.07. The intercepts and random effects are estimated differently.

## 5) Constrain the residual variances to be equal. Does this change the fit of your model?

```{r}
model.8 <- 'neuro_i =~ 1*neuro_7t + 1*neuro_8t + 1*neuro_9t + 1*neuro_10t
            neuro_s =~ 0*neuro_7t + 1*neuro_8t + 2*neuro_9t + 3*neuro_10t

neuro_7t ~~ u*neuro_7t
neuro_8t ~~ u*neuro_8t
neuro_9t ~~ u*neuro_9t
neuro_10t ~~ u*neuro_10t'
fit.8 <- growth(model.8, data = oysup)
summary(fit.8)
fitMeasures(fit.8)
```
Yep. These constraints are overly restrictive for the nature of this data across four years, and so the model becomes fully saturated and the cfi defaults to 1.

## 6) Contrain your slope to be fixed, not random. How does this change your model?

```{r}
model.9 <- 'neuro_i =~ 1*neuro_7t + 1*neuro_8t + 1*neuro_9t + 1*neuro_10t
            neuro_s =~ 0*neuro_7t + 1*neuro_8t + 2*neuro_9t + 3*neuro_10t
            neuro_s ~~ 0*neuro_s'
fit.9 <- growth(model.9, data = oysup)
summary(fit.9)

anova(fit.6, fit.9)
```

Honestly, not much changed, but there wasn't much variation in the slope to begin with. Now, the slope's variance is constrained to zero, whereas before, it was estimated at -.05 (basically zero). The intercept increased by a teeny tiny bit, and the magnitude of the (negative) fixed slope became a teeny tiny bit larger. However, the intercept variance did increase from .23 to .37, likely because that extra variance has to go somewhere!

## 7) Change the time metric in your SEM growth model. How does that change your estimates? Does it change your fit statistics?

```{r}
model.10 <- 'neuro_i =~ 1*neuro_7t + 1*neuro_8t + 1*neuro_9t + 1*neuro_10t
            neuro_s =~ 1*neuro_7t + 2*neuro_8t + 3*neuro_9t + 4*neuro_10t'
fit.10 <- growth(model.10, data = oysup)
summary(fit.10)
fitMeasures(fit.10)
```
The estimate of the slope did not change; however, the estimate of the intercept and its variance did.

## 8) Try a different type of estimation (see lavaan tutorial for details). How does that change your model?

```{r}

```


## 9) Provide semplots for each of the models.

```{r}

```


## 10) Test measurement invariance across time for your construct. Can you run growth models? If there is evidence of non-invariance, what seems to be the problem?

```{r}

```


## 11) Fit a second order growth model. Compare and contrast the estimates with the normal latent growth model.

```{r}

```


## 12) Fit a series of multiple group models. Constrain some parameters and compare the fit.

```{r}

```

mod.8 <- 'neuro_t1 =~ TPER7_08 + TPER7_10 + TPER7_17R + TPER7_12R + TPER7_13R
neuro_t2 =~ TPER8_08 + TPER8_10 + TPER8_17R + TPER8_12R + TPER8_13R
neuro_t3 =~ TPER9_08 + TPER9_10 + TPER9_17R + TPER9_12R + TPER9_13R
neuro_t4 =~ TPER10_08 + TPER10_10 + TPER10_17R + TPER10_12R + TPER10_13R

TPER7_08 ~~ TPER8_08 + TPER9_08 + TPER10_08
TPER8_08 ~~ TPER9_08 + TPER10_08
TPER9_08 ~~ TPER10_08

TPER7_10 ~~ TPER8_10 + TPER9_10 + TPER10_10
TPER8_10 ~~ TPER9_10 + TPER10_10
TPER9_10 ~~ TPER10_10

TPER7_17R ~~ TPER8_17R + TPER9_17R + TPER10_17R
TPER8_17R ~~ TPER9_17R + TPER10_17R
TPER9_17R ~~ TPER10_17R

TPER7_12R ~~ TPER8_12R + TPER9_12R + TPER10_12R
TPER8_12R ~~ TPER9_12R + TPER10_12R
TPER9_12R ~~ TPER10_12R

TPER7_13R ~~ TPER8_13R + TPER9_13R + TPER10_13R
TPER8_13R ~~ TPER9_13R + TPER10_13R
TPER9_13R ~~ TPER10_13R

TPER7_08 ~~ u*TPER7_08
TPER7_10 ~~ u*TPER7_10
TPER7_17R ~~ u*TPER7_17R
TPER7_12R ~~ u*TPER7_12R
TPER7_13R ~~ u*TPER7_13R
TPER8_08 ~~ u*TPER8_08
TPER8_10 ~~ u*TPER8_10
TPER8_17R ~~ u*TPER8_17R
TPER8_12R ~~ u*TPER8_12R 
TPER8_13R ~~ u*TPER8_13R
TPER9_08 ~~ u*TPER9_08
TPER9_10 ~~ u*TPER9_10
TPER9_17R ~~ u*TPER9_17R
TPER9_12R ~~ u*TPER9_12R
TPER9_13R ~~ u*TPER9_13R
TPER10_08 ~~ u*TPER10_08
TPER10_10 ~~ u*TPER10_10
TPER10_17R ~~ u*TPER10_17R
TPER10_12R ~~ u*TPER10_12R
TPER10_13R ~~ u*TPER10_13R'
