---
title: "Homework 2"
author: "Leah Schultz"
date: "9/28/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Chapter 3: Growth Curves
```{r loading, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(lme4)
library(ggplot2)
library(broom)
library(merTools)
purpose <- read.csv("~/Dropbox/Lab & Research/OYSUP Project/oysup_teacher_self.csv")
```

First, restructuring data:


```{r}
purpose_long <- tbl_df(purpose) %>%
  gather(-c(FAMID, SEX2, MEDUC2, MPEDUC2), key = "grade", value = "value") %>%
  separate(grade, into = c("variable", "grade"), sep = "_", convert = T) %>%
  spread(variable, value)

purpose_long_elem <- purpose_long %>% 
  filter(grade != 21)
```

## 1. Run linear models on all of your subjects (a basic regression). What is the average intercept, the average slope?

```{r}
model1 <- lm(cbmom ~ grade, data = purpose_long)
summary(model1)
```

Average intercept = 1.28

Average slope = .08

## 2. Now run a mlm/lmer model with only a random intercept.
```{r}
model2 <- lmer(cbmom ~ 1 + (1 | FAMID), data = purpose_long)
summary(model2)
```

## 3. What is the ICC?

ICC = % between- vs. within-person variance

variance by ID / variance by ID + residual variance

.64 / (.64 + 1.30) = .33


## What does residual variance look like compared to linear model? Create a graph to show this effect.

```{r warning=FALSE}
model1.aug <- augment(model1)
model2.aug <- augment(model2)
mod1_resid <- abs(model1.aug$.resid)
mod2_resid <- abs(model2.aug$.resid)
mean_mod1 <- mean(mod1_resid)
mean_mod2 <- mean(mod2_resid)
resid_df <- data.frame("Type" = c("Linear", "Mixed"), 
                       "Mean" = c(mean_mod1, mean_mod2))
resid_plot <- ggplot(resid_df, aes(x = Type, y = Mean)) +
  geom_col(width = .5)
resid_plot
```

Absolute value of the average residual variance is lower in the mixed model, since we're accounting for individual-level, random effects.

## 3. Introduce a fixed slope term. What is the difference in terms of the fixed effects estimates between this estimate and the previous? Of the residual standard error? Create a graph to show both fixed effects estimates and the CIs around them.

```{r}
model3 <- lmer(cbmom ~ grade + (1 | FAMID), data = purpose_long)
summary(model3)
```

Fixed effect estimate for intercept decreased from 1.60 to 1.32.

## 4. Run an additional model with a random slope. How does this change compare to the previous model? Should you keep the random slope or not?

```{r}
model4 <- lmer(cbmom ~ grade + (1 + grade | FAMID), data = purpose_long)
summary(model4)
```

## 5. Interpret the correlation between the slope and the intercept.

Correlation between slope and intercept = -.89. 

## 6. Create a density plot of the random effects from your final model.

```{r}
random_params <- tidy(model4, effect = "ran_modes")

raneff_plot <- ggplot(random_params, aes(x = estimate, color = term)) +
  geom_density()

raneff_plot
```

## 7. Create a caterpillar plot of the random effects. Is there any person that seems odd in terms of a large standard errors around intercept and slope estimates?

```{r}
re.sim <- REsim(model4)
plotREsim(re.sim)
```

## 8. Create a plot of the trajectory, along with a spaghetti plot of each person’s individual slope. Set the alpha level (transparency) on the individual slopes to make them easier to see.

```{r warning=FALSE}
predict <- predictInterval(merMod = model4, newdata = purpose_long_elem,
                           level = 0.9, n.sims = 100, 
                           stat = "median", include.resid.var = TRUE)
growth_df <- cbind(purpose_long_elem, predict$fit)

growth_plot <- ggplot(purpose_long_elem, aes(x = grade, y = predict$fit)) +
  geom_line(aes(group = FAMID), alpha = .2) +
  stat_smooth(method = lm) +
  theme_bw()+
  xlab("Grade")+
  ylab("Child-reported conflict with mother")
growth_plot
```

